---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nyczips

<!-- badges: start -->
<!-- badges: end -->

Provides a tibble of New YorK City zip codes and a simple features collection of their ZCTA polygons.

## Installation

You can install the development version of nyczips like so:

``` r
remotes::install_github("kjhealy/nyczips)
```

## Example


```{r example}
library(tidyverse)
library(sf)
library(nyczips)

nyc_zips


nyc_zip_sf
```


Notice that we have more zip codes in `nyc_zips` than zctas in `nyc_zip_sf`. Several of these zip codes are for PO Boxes or otherwise non-residential (like LGA and Fort Totten Park).

```{r}
nyc_zip_sf |> 
  filter(pop == 0)
```


With all the zips:

```{r}
ggplot(nyc_zip_sf) + geom_sf() + theme_void()
```


Without the zero-pops:

```{r}
nyc_zip_sf |> 
  filter(pop != 0) |> 
  ggplot() + 
  geom_sf() + 
  theme_void()
```


Zero-pops highlighted:

```{r}
nyc_zip_sf |> 
  mutate(empty = ifelse(pop == 0, TRUE, FALSE)) |> 
  ggplot() + 
  geom_sf(aes(fill = empty)) + 
  scale_fill_manual(values = c("white", "red")) +
  theme_void()
```

